Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-03 wearables_survey.tex
wrote abstract, conclusion, ethics, and acknowledgements sections.

\begin{abstract}
(Okay, kind of intimidated with writing the abstract. My plan is to write intro/conclusion first and then condense it into here, while nodding off to the contributions that we made.) At the very least, I can say that we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices. Data type, data recipient, and device type all matter different amounts. All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies. Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma. Fantastic ending sentence here.
\end{abstract}

@@

There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro} . However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.

@@

\section{Conclusion}
(REDO) END STRONG! Should I put this before the Discussion?  Echo the introduction a little, remind the people of the takeaways in a way that highlights the contribution of this paper. Intro: ``we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices. Data type, data recipient, and device type all matter different amounts. All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies. Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma. Fantastic ending sentence here.''

I can talk about the results a little bit more in depth because people have already supposedly read my whole paper now. Pull out the subtleties I couldn't have done in the introduction, and go into specific details, shooting out numbers and statistics. Then conclude the whole thing with an inspirational pitch on how there is much future work to be done in this area, how this area is exciting, and how I basically helped people see both of these things.

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
NSF funding, SCRUB, BLUES. Also any people who helped.

>>>>

\begin{abstract}
There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint. These works generally focus on X and Y. However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. We surveyed 2,250 users about 74 data types, 4 recipients, and 2 devices to show users' perceptions of a wide range of wearables threats in a wide range of scenarios, along with an evaluation of which factors contribute to the severity of a threat. We also asked participants to rate 20 new technologies, as well as asked for what they think is the most likely risk associated with wearables. Our ranking for concerns can be used to guide future research in wearables security, especially research regarding protecting sensitive data and effective notifications and indicators. 
\end{abstract}

@@

There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}. However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.

@@

\section{Conclusion}

We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices. Participants rated how upset they would be if 305 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns. We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model. An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology. We also state what users perceived as the most significant concerns with respect to wearable devices. We conclude by discussing future research directions in the wearables and user study space.

@@

%ACKNOWLEDGMENTS are optional
\section{Research Ethics} 
We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study. Survey data was collected in an anonymous manner. Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.

\section{Acknowledgments}
The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research. Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings. Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
